Writing a reproducible paper with Quarto

### 2023-02-17 paper.qmd
Update some cross-references.

To see how referencing works simply see the different examples for figures, tables and sections below. For instance in Section \@ref(sec:tables) you can find different ways of referencing tables. The code of the underlying `paper.qmd` will show you how I referenced Section \@ref(sec:tables) right here namely with '`Section \@ref(sec:tables)`'.

@@

# Tables {#sec:tables}

@@

A great function is `kable()` (`knitr` package) in combination with `kableExtra`. @tbl-2 provides an example. To reference the table produced by the chunk you need to add `#| label: tbl-x` at the start of the chunk, i.e., `#| label: tbl-2` and would reference it by adding "`@tbl-2`" in your text.

 {{

```{r table-2, echo=TRUE}
#| label: tbl-2
#| tbl-cap: "Summary: Numeric variables"

@@

@tbl-3 shows a summary table for numeric variables.

```{r table-3, echo=TRUE}
#| label: tbl-3
#| tbl-cap: "Summary: Numeric variables"

@@

@tbl-4 shows a summary table for categorical variables.

```{r table-4, echo=TRUE}
#| label: tbl-4
#| tbl-cap: "Summary: Categorical variables"

@@

@tbl-5 shows the output for a regression table. Make sure you name all the models you estimate (even if its 50) and explicitly refer to model names (M1, M2 etc.) in the text.

```{r}
#| label: tbl-5
#| tbl-cap: "Linear regression"

>>>>

To see how referencing works simply see the different examples for figures, tables and sections below. For instance in @sec-tables you can find different ways of referencing tables. The code of the underlying `paper.qmd` will show you how I referenced @sec-tables right here namely with '`@sec-tables`' whereas the corresponding section title was assigned the corresponding label '`# Tables {#sec-tables}`'.

@@

# Tables {#sec-tables}

@@

A great function is `kable()` (`knitr` package) in combination with `kableExtra`. @tbl-2 provides an example. To reference the table produced by the chunk you need to add `#| label: tbl-x` at the start of the chunk, i.e., `#| label: tbl-1` and would reference it by adding "`@tbl-1`" in your text. See below for the full chunk code (the one that actually produces the table is hidden).

```{{r}}
#| label: tbl-1
#| tbl-cap: "Summary: Numeric variables"

kable(swiss[1:5,], row.names = TRUE, 
      caption = 'Table with kable() and kablestyling()', 
      format = "html", booktabs = T) %>%
        kable_styling(full_width = T, 
                      latex_options = c("striped", 
                                        "scale_down",
                                        "HOLD_position"),
                      font_size = 11)
```

```{r table-2, echo=FALSE}
#| label: tbl-1
#| tbl-cap: "Summary: Numeric variables"

@@

@tbl-2 shows a summary table for numeric variables.

```{r table-3, echo=TRUE}
#| label: tbl-2
#| tbl-cap: "Summary: Numeric variables"

@@

@tbl-3 shows a summary table for categorical variables.

```{r table-4, echo=TRUE}
#| label: tbl-3
#| tbl-cap: "Summary: Categorical variables"

@@

@tbl-4 shows the output for a regression table. Make sure you name all the models you estimate (even if its 50) and explicitly refer to model names (M1, M2 etc.) in the text.

```{r}
#| label: tbl-4
#| tbl-cap: "Linear regression"
